%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[a4paper, 12pt]{article}
\usepackage{enumitem} % for leftmargin of itemize
\usepackage{fancyhdr} % allows fancy headers
\usepackage{lastpage} % get the last page number
\usepackage{sectsty} % for section styling like header font size

% LAYOUT %
% Font
%% Set \header command
\makeatletter
\newcommand\header{\@setfontsize\Huge{16}{16}} % for my name
\makeatother

%% Edit \section font size
\sectionfont{\fontsize{12}{12}\selectfont}

% Margins
\usepackage[margin=1in]{geometry} % for page margin

% Indentation
\setlength\parindent{.5in}

% Page Numbering
%\pagenumbering{gobble}

% Table
\setlength{\arrayrulewidth}{0mm}
\setlength{\tabcolsep}{1pt}


% DOCUMENT %
\begin{document}
\thispagestyle{empty}

\pagestyle{fancy}
\rhead{Michael L. Otte, Page \thepage { of} \pageref{LastPage}}

\noindent
\textbf{\header Michael L. Otte}
\vspace{-3mm}

\noindent
\line(1,0){452}\\[1mm]
\begin{tabular}{ |p{2.9in}|p{3.75in}| }
% & {\sl LinkedIn:} www.linkedin.com/in/michaelotte13 \\[0mm]
{\sl Email:} MichaelOtte1@gmail.com & {\sl Cell:} (831) 704-6563 \\[3mm]
\end{tabular}\\[-3mm]

\noindent Freenome, Inc.\\
A Computational Genomics, Non-Invasive Cancer Diagnostics, and Liquid Biopsy Co.\\
201 Gateway Blvd\\
South San Francisco, CA 94080

\section*{CURRENT POSITION}
\vspace{-3mm}
{\bf Freenome, Inc.}\hfill South San Francisco, CA\\
Senior Software Engineer\hfill September 2015-Present

\section*{EDUCATION}
\vspace{-3mm}
{\bf Dartmouth College}, Hanover, NH \hfill June 2013 \\[-7mm]
\begin{itemize}[leftmargin=5mm] 
\itemsep -1mm
	\item[] {\sl B.A.} {Socio-Cultural Anthropology (Honors Student with Research Grant)}
	\item[] {\sl Coursework and Research completed for degree in} {Biology, Immunology Concentration}
	\item[] {\sl Coursework completed for} {Pre-Medicine Requirements}
\end{itemize}

\section*{GRANTS AND AWARDS}
\vspace{-3mm}
{\bf Honors Citation in Anthropology, Professor James Igoe}\hfill August 2012\\
Dartmouth College\\[2mm]
{\bf C. Everett Koop Scholar}\hfill November 2011\\
Dartmouth Center on Addiction, Recovery \& Education\\[2mm]
{\bf Honors Citation in Anthropology, Chair Dale Eickelman}\hfill August 2011\\
Dartmouth College\\[2mm]
{\bf Howard Hughes Medical Institute Scholar Research Grant}\hfill July 2011\\
The Howard Hughes Medical Institute\\[2mm]
{\bf Claire Garber Goodman Research Grant}\hfill May 2011\\
Dartmouth College\\[2mm]
{\bf Dartmouth Keenan Family Scholar}\hfill January 2009\\
Dartmouth College

\section*{RESEARCH EXPERIENCE}
\vspace{-3mm}
{\bf Freenome}{, South San Francisco, CA}\hfill {\bf September 2015-Present \\}
{\sl CTO, VP of Product, Software Engineer - freenome.com} \\[-7mm]
\begin{itemize}[leftmargin=5mm]
\itemsep -2pt
	\item Conducted research in classification and biomarker discovery in cancer research via cloud-based computing of cell-free DNA (cfDNA).
	\item Heavily involved in high-throughput bioinformatics work on next-generation sequencing data from raw read data to analysis.
	\item Developed an in-house next-generation sequencing laboratory information management system (LIMS).
	\item Developed a drag-and-drop genome browser for genetic variant analysis.\\
	\item Co-authored grants (National Science Foundation) and was involved in manuscript writing on cell-free DNA analysis.
	\item Conducted academic collaborations with labs from Massachusetts General Hospital, UCSD, UCSF, and others.
\end{itemize}
                 
\noindent
{\bf Dartmouth-Hitchcock Medical Clinic}{, Lebanon, NH}\hfill {\bf May 2011-August 2013 \\}
{\sl Undergraduate Researcher - geiselmed.dartmouth.edu/rigby/}\\
Immunological mechanisms and effects of Rituximab on B cell depletion\\[-6mm]
\begin{itemize}[leftmargin=5mm] 
\itemsep -2pt
	\item Studied the effects of rituximab (a.k.a. rituxan) in depletion of B cells via antibody-mediated cell shaving and complement dependent cell cytotoxicity
	\item Performed over 100 laser flowcytometry experiments through the entire process from experimental design to analysis and QA/QC
	\item Techniques included assay prep, PBMC and sera isolation from whole blood, cell carrying, basic microscopy and staining (e.g. ethidium bromide staining), and laser flow cytometry
	\item Resulting paper: {\sl Induction of interleukin-6 production by rituximab in human B cells.} doi: 10.1002/art.38798 (not a listed co-author)
\end{itemize}

\noindent
{\bf Dartmouth College}{, Hanover, NH}\hfill {\bf May 2011-June 2013 \\}
{\sl Undergraduate Researcher - Ethnographic Research}\\
The Way of the True Pilgrim: Finding Meaning on the Camino de Santiago\\[-6mm]
\begin{itemize}[leftmargin=5mm] 
\itemsep -2pt
	\item Conducted ethnographic field work for 3 months, hiking about 1,000 miles of the St. James Way pilgrimage road in France and Spain.
	\item Completed literature research on topic of pilgrimage in English and Spanish.
	\item Studied the group effects of pilgrims on the "Camino de Santiago" (the St. James Way), a historically, Roman Catholic pilgrimage in the field.
	\item Conducted in-field ethnographic research, including surveys, interviews, group discussions, observational field notes, and recordings.
\end{itemize}

\section*{RELATED EXPERIENCE}
\vspace{-3mm}
\noindent
{\bf C. Everett Koop Institute}{, Hanover, NH}\hfill {\bf June 2012-June 2013 \\}
{\sl Personal Assistant to Dr. C. Everett Koop}\\[-6mm]
\begin{itemize}[leftmargin=5mm] 
\itemsep -2pt
	\item Organized speaker events with prominent physicians and policymakers including Dr. Samuel Kessel.
	\item Answered emails and coordinated meetings for the former surgeon general. 
	\item Helped coordinate the funerary event at Dartmouth College for Dr. C. Everett Koop.
\end{itemize}

\noindent
{\bf National Registry of Emergency Medical Technicians}\hfill {\bf Aug 2010-March 2015 \\}
{\sl Emergency Medical Technician}\\
{Multiple Locations including Haiti, California, New Hampshire}\\[-6mm]
\begin{itemize}[leftmargin=5mm] 
\itemsep -2pt
	\item Opened up free clinics in rural areas of Haiti with a U.S. disaster relief team of doctors and nurses after the catastrophic 2010 earthquake.
	\item Constructed and installed a natural "biodigester" to provide cooking gas for a rural Haitian village.
	\item Worked over 100+ hours responding and staying on-call as a first responder in New Hampshire.
	\item Interacted with medical personnel and patients in a U.S. clinic as a clinical medical technician.
	\item Nationally, California, and New Hampshire certified as an emergency medical technician and basic life support instructor.
	\item Certified in emergency crisis management by Emergency Management Institute of the U.S. Department of Homeland Security and FEMA.
\end{itemize}
                 
\section*{SOFTWARE EXPERIENCE}
\noindent
\begin{tabular}{ | p{40mm} | p{40mm} | p{40mm} | p{40mm} }
Python & Javascript & HTML5+CSS3 & PostgreSQL\\[2mm]
MySQL & shell scripting & Nginx+Gunicorn & Java\\[2mm]
C++ & PHP & Word/Excel/Powerpoint
\end{tabular}\\[-1mm]
                 
\section*{INTERESTS}
\vspace{-3mm}
\begin{itemize}[leftmargin=5mm] 
\itemsep -2pt
	\item I enjoy contributing to open/free source software projects (e.g. Airflow), conducting biological and ethnographic research, rock climbing, surfing, singing, and volunteering.
	\item I started coding in Hypercard when I was 10 and donated my proceeds to charities.
	\item I used to be a member of the Greater Philadelphia Chamber of Commerce.
\end{itemize}

                
\end{document}